6.829 Final Project: A comparison of bit rate selection algorithms

### 2013-08-06 paper/paper.tex

One of the key ways that wireless networks differ from wired links is
that wireless networks have varying link rates.  Link conditions vary
with time due to interference from other devices, changing network
geometry, and mobile clients.  An optimal rate at one time may be
different from the optimal rate just 30 seconds earlier.  A good
bit rate selection algorithm has to detect and adapt to these
conditions.  If the chosen bit rate is too slow, then the throughput
will be unnecessarily low; if the rate is too high, failures will be
very frequent and throughput will again suffer.

@@

This paper will provide a general overview of SampleRate and Minstrel.
We then discuss our testing methodology.  We compare the performance
of the two algorithms, and then discuss modifications we made to
Minstrel and compare its performance to the current kernel
implementation.

@@

SampleRate, first introduced in \cite{samplerate}, is a bit rate
selection algorithm which maintains estimates of average transmission
time for each potential bit rate.To keep these estimates up to date,
SampleRate periodically sends a packet at a randomly-selected bit
rate, and uses the success or failure of this packet to update the
average transmission time of that bit rate.  SampleRate also abandons
a bit rate after four successive failures at that rate.  All
information about packets is maintained with a 10-second sliding window.

@@

Minstrel makes use the multi-rate retry chain (MRR), an array of bit rates
and number of attempts to make at each bit rate, that tells the card
which rates to try before reporting a failure.  The retry chain makes
failures extremely unlikely and allows Minstrel to choose fall-back
rates when a packet does not succeed.  Minstrel sets the MRR to first
try the rate with the highest throughput, then the next-highest
throughput, then greatest probability of success, and finally attempts
to send a packet at the lowest, base rate.  In essence, Minstrel tells
the card to send at the highest throughput rates but to fall back to
reliable rates upon failure.

To keep an accurate estimate of throughput and probability for each
rate, Minstrel sends sample frames ten percent of the time.  However,
Minstrel tries to avoid sampling at a rate slower than the current
best rate, if the current best rate is still successfully
transmitting.  If the randomly chosen rate has a higher lossless
throughput than the current optimal rate, the MRR first lists the
sample rate, then the highest-throughput rate, then the
best-probability rate, and finally the base rate.  On the other hand,
if the random rate is slower than the optimal rate, the sample rate is
placed lower in the retry chain: first, the best throughput rate is
tried, and only if it fails does the sample rate then get attempted
(followed, as usual, by the best probability rate and the base rate).
This ensures that Minstrel never samples rates worse than the current
optimal rate unless the optimal rate experiences a failure.  See
Table~\ref{table:mrr} for an overview of the retry chains used in
Minstrel.

@@

The probability $p$ of a successful transmission is calculated from
statistics collected by the \texttt{ProcessFeedback()} method, and is
done using an exponential weighted moving average, or EWMA.  The EWMA
creates a weighted average that weighs recent data more heavily than
old data, with the weighting for old data decreasing exponentially.
An EWMA ensures that a sudden degradation in link quality will create
a rapid response in the probabilities, making the EWMA-using Minstrel
perform better in dynamic environments.  Minstrel will waste less time
sending packets at a rate that no longer works, as compared to a
simple sliding-window probability calculation.

@@

Our initial plan was to use the algorithms as implemented in the
MadWifi drivers for the Atheros chip.  However, MadWifi is deprecated,
and only runs on now-ancient network cards.  In addition to the
unavailability of compatible hardware, MadWifi would not be an
accurate reflection of contemporary users.  Both ath5k and
\texttt{ath9k}, which were created to replace MadWifi, did not port
the old bit rate selection system from MadWifi and instead opted to
use the Linux kernel's rate selection framework, which only implements
Minstrel.  Porting SampleRate over to the new drivers would not have
been trivial, as there are vast differences in the assumed interfaces.

@@

Traces were collected from an \texttt{ath9k} driver modified to sample
bit rates uniformly (forgoing the usual bit rate selection algorithm)
and to report successes and failure from each packet.  Each bit rate
was sampled uniformly in time -- thus, more packets were sent at
higher bit rates, since those bit rates otherwise deliver packets
faster.  For each packet sent, the time to send was recorded, and the
bit rate for the next packet was chosen to be the bit rate that had
the smallest total transmissions time.  This guarantees approximately
uniform selection of bit rates.  The wireless card used was an
Qualcomm Atheros \texttt{AR9285} Wireless Network Adapter.

Traces were collected at an unused access point in a basement of MIT.
Before initiating trace collection, the wireless card was put in
monitor mode for a minute to check that no other users were connected
to the access point.  None were, guaranteeing that traces would not
include delays from carrier sensing or run into problems due to
congestion at the access point.  Traffic was simulated by sending 1500
byte packets to the access point's IP address.  Packets were sent over
UDP to avoid the TCP congestion window and retry loop; since no users
were using the access point, there was no real risk of deteriorating
service for other users.  Figure~\ref{figure:1} shows a floor plan of
the access point and basement.

@@

Once collected, traces were fed to a bit rate selection simulator to
analyze the performance of Minstrel and SampleRate.  Both algorithms
were represented by two functions: \texttt{ApplyRate}, which returned
a multi-rate retry chain of rates to attempt transmission at, and
\texttt{ProcessFeedback}, which was passed the success or failure of
the transmission and how many attempts were made at each bit rate
(along with the current time and the total time to send the packet);
this parallels the interface used by the Linux kernel itself.  Helper
functions, like SampleRate's \texttt{RemoveStaleResults} function,
were instead called from one of \texttt{ApplyRate} or
\texttt{ProcessFeedback}.  For every packet transmission, the
simulator would call \texttt{ApplyRate}; compute the probability of
success based on packets sent in 10-millisecond window around the
current time; and from that determine the success or failure of the
packet, and the number of retries required.  The results of a test run
are thus non-deterministic; both algorithms tested are
non-deterministic anyway, so this is no handicap.  To improve
re-implementation fidelity, both implementations were meticulously
checked by both authors.

@@

@@

Minstrel and SampleRate perform similarly, usually within 3 Mbps of
each other.  In especially noisy situations, such as when the client
is moving or when the client is around the corner from the access
point, Minstrel consistently outperforms SampleRate.
Figure~\ref{figure:3} shows the results of a single run of both
Minstrel and SampleRate over all the different types of traces we
collected.  This is consistent with the literature---the authors of
Minstrel noted that they focused on making Minstrel robust to poor
conditions~\cite{minstrel}, which means losing potential throughput
gains in stable situations.  Conversely, John Bicket noted that
SampleRate performs better in stable situations than noisy or highly
varying conditions~\cite{samplerate}.  We were slightly surprised to
see how significantly SampleRate outperformed Minstrel in certain
situations, though, with throughput being up to $67\%$ higher.

@@

In Figure~\ref{figure:2} we show the performance of constant bit rates
on the \texttt{clear\_1.dat} trace, which is a 35 second trace in
clear view of the access point.  The optimal rate here was 18 Mbps,
which achieved an average throughput of about 15 Mbps.  The next
highest bit rate, 24 Mbps, shows a large plummet in performance, down
to a throughput of 1.17 Mbps.  This steep drop is characteristic, and
is also talked about in the SampleRate thesis~\cite{samplerate}.  It
demonstrates just how important bit rate selection is---the optimal
bit rate has typically much higher throughput than the next-best rate,
but if the algorithm strays too high the results can be devastating.

@@

Bit rate selection algorithms naturally show variation between runs on
the same data because probe rates are chosen randomly.  The variations
were small, though.  On ten runs on the \texttt{clear\_1.dat} trace,
the average of Minstrel over 10 runs was 7.52 Mbps, with a maximum
variation of +/- 0.12 Mbps.  SampleRate was similarly stable, it
averaged 5.284 Mbps over 10 runs, with a maximum variation of about
+/- 0.3 Mbps.  The variation of results on other traces (except the
very short traces, where variance was naturally higher) was similar.

The histograms of which rates the algorithms decided to send at
provided some useful insight into their behavior.  Table~\ref{table:2}
is a histogram of a 35 second corner trace.  In this situation
Minstrel outperforms SampleRate.  The constant rate throughputs
demonstrate that 11, 12 and 18 Mbps were the optimal rates to send at,
and that no packets were successful at any higher rates.  SampleRate
does not use these rates except for probe packets, which happens once
every ten seconds.  Minstrel, since it does not terminate transmission
after four successive failures, spends a lot of time sending probe
packets at these high rates, which are never successful.  The only
reason low rates have fewer probe packets is because Minstrel
explicitly places them second in the retry chain, and because the main
rate usually succeeds.  Despite the fact that SampleRate spends less
time probing high rates, it is less successful.  This is because
Minstrel send the most packets at the three most successful bit rates.
SampleRate, however, spends too much time sampling low bit rates.
Additionally, it spends a lot of time sending at 5.5 Mbps.  We suspect
that this might be because the equation SampleRate uses to estimate
average transmission time needs to be tweaked.
%   TODO: why does SampleRate spend time at 5.5 Mbps???

Our examination of the histograms showed us that Minstrel spends a lot
of time sampling at high rates.  In the specific case we examined, they
were all probe packets.  But sometimes Minstrel would choose 54 Mbps as
the rate with the best throughput, which made little sense.  A closer
investigation revealed that Minstrel would sometimes get lucky with a
successful probe at 54 Mbps.  The probability of success would be 1, so
then 54 Mbps would be chosen as the rate with the best throughput.  This
is unfortunate, but the real harm comes in the next window: packets
would now be send at 54 Mbps, and nearly all would fail.  However,
since these hundreds of failed packets weight equally with the single
successful probe packet, Minstrel still considers 54 Mbps the best
rate.  Thus the probability of success might drop from 1 to about 0.70,
which is still high enough for the throughput equation to rank 54 Mbps
highly.  Fundamentally, the problem is that the EWMA does not account
the second block having hundreds more packets than the first.  In the
next section we will talk about Minproved, an improved version of
Minstrel where we attempt to fix this problem.

@@

To achieve, this weighing, we first recast the usual EWMA algorithm.
The usual algorithm computes $$p \gets \alpha p + (1 - \alpha)
\frac{n_i}{d_i}),$$ where $p$ is the EWMA probability, $\alpha$ is a
weight factor equal to $0.75$ in Minstrel, and $n_i$ and $d_i$ are the
number of successful and total packets in the 100ms window.  We next
write this as $$p \gets \frac{\beta p + \frac{n_i}{d_i}}{\beta + 1},$$
where $\beta = \alpha / (1 - \alpha)$.  We can now change the factor
in front of $n_i / d_i$ to account for the total number of packets
sent.  In our case, we chose to compute $$p \gets \frac{\beta p + w_i
  \frac{n_i}{d_i}}{\beta + w_i},$$ where the weight $w_i$ is $d_i / (d
/ b)$, with $d$ the total number of packets ever send and $b$ the
total number of 100ms windows ever seen.  Then $d / b$ is the average
number of packets per window and $d_i / (d / b)$ is the ratio between
the current window and the average window.  Note that if the current
window is of average size, this is exactly equal to the usual EWMA
result.  Finally, we can simplify the above equation to $$S p \gets
\frac{\beta \frac{d}{b} S p + S n_i}{\beta \frac{d}{b} + d_i},$$ where
$S$ is any constant.  This equation is usable in fixed-point
arithmetic (where $S$ is the scaling factor for the fixed-point
representation), making it suitable for implementation in the Linux
kernel (which avoids floating point computations for
portability reasons).  Because packets are high rates rarely succeed,
the average window size is a few packets; thus, the main qualitative
difference between our balanced EWMA and the original Minstrel EWMA is
that non-probe packets at probe bit rates are weighed extraordinarily
heavily, and this fact allows us to avoid multiple failing 100ms
windows.

@@

We noted another curious fact about Minstrel: the kernel
implementation of Minstrel samples rates very frequently.  This is due
to a flag the kernel uses to track which probe bit rates were actually
sampled.  In cases where the probe packets are at a lower bit rate
than the current bit rate, the probe packets might never be sent if
the current bit rate succeeds.  However, the flagging seems to
misbehave in certain cases, causing the extremely aggressive probing
we see in some traces.  For example, in one of the traces where the
client was around a corner from the access point, Minstrel sent almost
half of its packets at probe frequencies.  We modified Minstrel to be
less aggressive with probe packets, decreasing the sampling frequency
to approximately 10\%.  This lead to more improvement, especially on
noisy traces such as the cases where the client was around a corner or
moving.

>>>>

One of the key ways that wireless networks differ from wired is
that wireless networks have varying link rates.  Link conditions vary
with time due to interference from other devices, changing network
geometry, and mobile clients.  An optimal rate at one time may be
different from the optimal rate just 30 seconds earlier.  A good
bit rate selection algorithm has to detect and adapt to these
conditions.  If the chosen bit rate is too slow, then the throughput
will be unnecessarily low; if the rate is too high, failures will be
very frequent and throughput will again suffer.

@@

@@

SampleRate, first introduced in \cite{samplerate}, is a bit rate
selection algorithm which maintains estimates of average transmission
time for each potential bit rate. To keep these estimates up to date,
SampleRate periodically sends a packet at a randomly-selected bit
rate, and uses the success or failure of this packet to update the
average transmission time of that bit rate.  SampleRate also abandons
a bit rate after four successive failures at that rate.  All
information about packets is maintained with a 10-second sliding window.

@@

Minstrel makes use the multi-rate retry chain (MRR), an array of bit rates
and number of attempts to make at each bit rate, that tells the card
which rates to try before reporting a failure.  The retry chain makes
failures extremely unlikely and allows Minstrel to choose fall-back
rates when a packet does not succeed.  When not sending a probe packet,
Minstrel sets the MRR to first try the rate with the highest throughput, 
then the next-highest throughput, then greatest probability of success, 
and finally attempts to send a packet at the lowest base rate.  
In essence, Minstrel tells the card to send at the highest throughput 
rates but to fall back to reliable rates upon failure.

To keep an accurate estimate of throughput and probability for each
rate, Minstrel sends sample frames ten percent of the time.  However,
Minstrel tries to avoid sampling at a rate slower than the current
best rate.  If the randomly chosen rate has a higher lossless
throughput than the current optimal rate, the MRR first lists the
sample rate, then the highest-throughput rate, then the
best-probability rate, and finally the base rate.  On the other hand,
if the random rate is slower than the optimal rate, the sample rate is
placed lower in the retry chain: first, the best throughput rate is
tried, and only if it fails does the sample rate then get attempted
(followed, as usual, by the best probability rate and the base rate).
This ensures that Minstrel never samples rates worse than the current
optimal rate unless the optimal rate experiences a failure.  See
Table~\ref{table:mrr} for an overview of the retry chains used in
Minstrel.

@@

The probability $p$ of a successful transmission is calculated from
statistics collected by the \texttt{ProcessFeedback()} method, and is
done using an exponential weighted moving average, or EWMA.  The EWMA
creates a weighted average that weighs recent data more heavily than
old data, with the weighting for old data decreasing exponentially.
An EWMA ensures that a sudden degradation in link quality will create
a rapid response in the probabilities, making Minstrel
perform better in dynamic environments.  Minstrel will waste less time
sending packets at a rate that no longer works, as compared to a
simple sliding-window probability calculation.

@@

Our initial plan was to use the algorithms as implemented in the
MadWifi drivers for the Atheros chip.  However, MadWifi is deprecated,
and only runs on very old network cards.  In addition to the
unavailability of compatible hardware, MadWifi would not be an
accurate reflection of contemporary users.  Both ath5k and
\texttt{ath9k}, which were created to replace MadWifi, did not port
the old bit rate selection system from MadWifi and instead opted to
use the Linux kernel's rate selection framework, which only implements
Minstrel.  Porting SampleRate over to the new drivers would not have
been trivial, as there are vast differences in the interfaces.

@@

Traces were collected from an \texttt{ath9k} driver modified to sample
bit rates uniformly and to report successes and failure from each packet.  
Each bit rate was sampled uniformly in time --- thus, more packets 
were sent at higher bit rates, since those bit rates deliver
packets faster. For each packet sent, we recorded the time it was sent,
the bit rate it was sent at, and whether or it it succeeded. The bit rate 
for the next trace packet was chosen to be the bit rate that had
the smallest total transmission time so far.  This guarantees approximately
uniform selection of bit rates.  The wireless card used was an
Qualcomm Atheros \texttt{AR9285} Wireless Network Adapter.

Traces were collected at an unused access point in a basement of MIT.
Before initiating trace collection, the wireless card was put in
monitor mode for a minute to check that no other users were connected
to the access point.  None were, guaranteeing that traces would not
include delays from carrier sensing or run into problems due to
congestion at the access point.  Traffic was simulated by sending 1500
byte packets to the access point's IP address.  Packets were sent over
UDP to avoid the TCP congestion window and retry loop. Figure~\ref{figure:1} 
shows a floor plan of the access point and basement.

@@

Once collected, traces were fed to a bit rate selection simulator to 
analyze the performance of Minstrel and SampleRate. 
\texttt{harness.py} interfaced with the bit-rate selection algorithms using
two functions: \texttt{ApplyRate()} and \texttt{ProcessFeedback()}.
\texttt{ApplyRate} returns a multi-rate retry chain of rates to attempt 
transmission at. The retry chain is one element long for SampleRate, since it
does not use MRR. \texttt{ProcessFeedback} is a callback that is passed 
the success or failure of the transmission and how many attempts were made
at each bit rate. This parallels the interface used by the Linux kernel 
itself. For every packet transmission, the simulator would call 
\texttt{ApplyRate}; compute the probability of success based on packets 
sent in 10-millisecond window around the current time; and from that 
determine the success or failure of the packet, and the number of retries 
it required.

@@

To improve re-implementation fidelity, both implementations were meticulously checked by both authors.

@@

Minstrel and SampleRate perform similarly, usually within 3 Mbps of
each other.  We were slightly surprised to
see how significantly SampleRate outperformed Minstrel in certain
situations, though, with throughput being up to $67\%$ higher.
However, in especially noisy situations, such as when the client
is moving or when the client is around the corner from the access
point, Minstrel consistently outperforms SampleRate.
Figure~\ref{figure:3} shows the results of a single run of both
Minstrel and SampleRate over all the different types of traces we
collected.  This is consistent with the literature---the authors of
Minstrel noted that they focused on making Minstrel robust to poor
conditions~\cite{minstrel}, which means losing potential throughput
gains in stable situations.  Conversely, John Bicket noted that
SampleRate performs better in stable situations than noisy or highly
varying conditions~\cite{samplerate}.

@@

In Figure~\ref{figure:2} we show the performance of constant bit rates
on the \texttt{clear\_1.dat} trace, which is a 35 second trace in
clear view of the access point.  The optimal rate here was 18 Mbps,
which achieved an average throughput of about 15 Mbps.  The next
highest bit rate, 24 Mbps, shows a large plummet in performance, down
to a throughput of 1.17 Mbps.  This steep drop is characteristic, and
is also talked about in the SampleRate thesis~\cite{samplerate}.  It
demonstrates just how important bit rate selection is --- the optimal
bit rate has typically much higher throughput than the next-best rate,
but if the algorithm strays too high the results can be devastating.

@@

Bit rate selection algorithms naturally show variation between runs on
the same data because probe rates are chosen randomly.  The variations
were small, though.  On ten runs on the \texttt{clear\_1.dat} trace,
the average of Minstrel over 10 runs was 7.52 Mbps, with a maximum
variation of +/- 0.12 Mbps.  SampleRate was similarly stable, it
averaged 5.284 Mbps over 10 runs, with a maximum variation of about
+/- 0.3 Mbps.  The variation of results on other traces (except for 
traces 5s or less) was similar.

The histograms of which rates the algorithms decided to send at
provided some useful insight into their behavior.  Table~\ref{table:2}
is a histogram of a 35 second corner trace.  In this situation
Minstrel outperforms SampleRate.  The constant rate throughputs
demonstrate that 11, 12 and 18 Mbps were the optimal rates to send at,
and that no packets were successful at any higher rates.  SampleRate
does not use these rates except for probe packets, which happens once
every ten seconds.  Minstrel, since it does not terminate transmission
after four successive failures, spends a lot of time sending probe
packets at these high rates, which are never successful.  The only
reason low rates have fewer probe packets is because Minstrel
explicitly places them second in the retry chain.
Despite the fact that SampleRate spends less
time probing high rates, it is less successful.  This is because
Minstrel send the most packets at the three most successful bit rates.
SampleRate, however, spends too much time sampling low bit rates.
Additionally, it spends a lot of time sending at 5.5 Mbps, which is not
one of the optimal rates.  We suspect
that this might be because the equation SampleRate uses to estimate
average transmission time needs to be tweaked.
%   TODO: why does SampleRate spend time at 5.5 Mbps???

Our examination of the histograms showed us that Minstrel spends a lot
of time sampling at high rates.  In the specific case we examined, they
were all probe packets.  But sometimes Minstrel would choose 54 Mbps as
the rate with the best throughput, which made little sense.  A closer
investigation revealed that Minstrel would sometimes get lucky with a
successful probe at 54 Mbps.  The probability of success would be 1, so
then 54 Mbps would be chosen as the rate with the best throughput.  This
is unfortunate, but the real harm comes in the next window: all non-probe 
packets would now be sent at 54 Mbps, and nearly all would fail.  However,
since these hundreds of failed packets weight equally with the single
successful probe packet, Minstrel still considers 54 Mbps the best
rate.  Thus the probability of success might drop from 1 to about 0.70,
which is still high enough for the throughput equation to rank 54 Mbps
highly.  Fundamentally, the problem is that the EWMA does not account
the second block having hundreds more packets than the first, so the 
probabilities were not declining fast enough after a large number of
   failures.

Additionally, Minstrel uses a complex method of calculating when to send 
a sample packet that involves a heuristic to make sure that 10\% of 
packets were actually samples. This is because the MRR places sample 
packets second in the retry chain when the sample rate is slower than 
the rate with the best throughput. So even if 10\% of probes have a 
sample rate in the retry chain, a sample rate is not actually sent 10\% 
of the time. We implemented this heuristic and it tended to cause 
Minstrel to send too many probe packets.

In the next section we will talk about Minproved, an improved version 
of Minstrel where we attempt to fix problems with EWMA and too-frequent
 probing.

@@

To achieve, this weighing, we first recast the usual EWMA algorithm.
The usual algorithm computes $$p \gets \alpha p + (1 - \alpha)
\frac{n_i}{d_i}),$$ where $p$ is the probability, $\alpha$ is a
weight factor equal to $0.75$ in Minstrel, and $n_i$ and $d_i$ are the
number of successful and total packets in the 100ms window.  We next
write this as $$p \gets \frac{\beta p + \frac{n_i}{d_i}}{\beta + 1},$$
where $\beta = \alpha / (1 - \alpha)$.  We can now change the factor
in front of $n_i / d_i$ to account for the total number of packets
sent.  In our case, we chose to compute $$p \gets \frac{\beta p + w_i
  \frac{n_i}{d_i}}{\beta + w_i},$$ where the weight $w_i$ is $d_i / (d
/ b)$, with $d$ the total number of packets ever sent and $b$ the
total number of 100ms windows ever seen.  Then $d / b$ is the average
number of packets per window and $d_i / (d / b)$ is the ratio between
the current window and the average window.  Note that if the current
window is of average size, this is exactly equal to the usual EWMA
result.  Finally, we can simplify the above equation to $$S p \gets
\frac{\beta \frac{d}{b} S p + S n_i}{\beta \frac{d}{b} + d_i},$$ where
$S$ is any constant.  This equation is usable in fixed-point
arithmetic (where $S$ is the scaling factor for the fixed-point
representation), making it suitable for implementation in the Linux
kernel (which avoids floating point computations for
portability reasons).  Because packets at high rates rarely succeed,
the average window size is a few packets.  The main qualitative
difference between our balanced EWMA and the original Minstrel EWMA is
that windows with many more packets than the average for that bit-rate are
weighted extraordinarily heavily. This fact allows us to avoid multiple 
failing 100ms windows.

@@

As noted in Section~\ref{sec:analysis}, Minstrel sends sample packets
too frequently. This is due to a flag the kernel uses to track whether
a probe bit rates was actually sampled. Recall that if the sample rate
is slower than the current best rate, it is second in the retry chain, 
so there is a good chance that the random rate will never be used to
send a packet. This system is used as an attempt to make sure that 10\%
of the sent packets are actually probes, as opposed to simply having 
10\% of packets contain a random rate somewhere in the retry chain.
 The flagging seems to misbehave, causing the extremely aggressive probing
we see in some traces.  For example, in one of the traces where the
client was around a corner from the access point, Minstrel sent almost
half of its packets at probe frequencies.  We modified Minstrel to be
less aggressive with probe packets. We eliminated the flagging system,
and instead simply put a random bit rate in 10\% of packets.
This lead to a very large throughput improvement, bringing Minstrel to
the same level of performance as SampleRate, and greatly exceeding it 
on noisy traces such as the cases where the client was around a corner or
moving. When this change was paired with the balanced EWMA change, it
consistently outperformed both vanilla Minstrel and SampleRate.
